\thetitle

### 2021-06-29 writing/mutate-mutators.tex
Add Christos's touch ups

Most of the mutators are self-explanatory.  The first six apply to all
gradually typed languages; the next six to those that include classes and
objects. The last four target distinguishing features of Typed Racket's type
system, specifically its sophisticated type system. For example, one mutation
produced by {\tt arithmetic} replaces a {\tt +} with a {\tt -} in an attempt to
change the type of the arithmetic expression; {\tt +}'s result is a {\tt
Positive-Integer} when all arguments are positive integers, while {\tt -}
yields {\tt Integer}~\citep{stathff-padl-12}. Similarly, the other three aim to
confound the occurrence type system. Figure~\ref{fig:negate-cond-example}
illustrates how this confusion works. The function deals with an input that is
either a {\tt Real} or {\tt \#false}; the conditional deals with the first type
in the {\tt then} branch and the second type in the {\tt else} branch.  If a
mutator wraps {\tt (not $\cdot$)} around the test of the conditional, the
resulting mutant no longer type checks and, when run, this function eventually
causes a run-time type check to signal an impedance mismatch.

>>>>

Most of the mutators are self-explanatory.  The first six apply to all
gradually typed languages; the next six to those that include classes and
objects. The last four target distinguishing features of Typed Racket's type
system, specifically its sophisticated type system. For example, one mutation
produced by {\tt arithmetic} replaces a {\tt +} with a {\tt -} in an attempt to
change the type of the arithmetic expression; {\tt +}'s result is a {\tt
Positive-Integer} when all arguments are positive integers, while {\tt -}
yields {\tt Integer}~\citep{stathff-padl-12}. Similarly, the other three aim to
confound the occurrence type system. Figure~\ref{fig:negate-cond-example}
illustrates how this confusion works. The function deals with an input that is
either a {\tt Real} or {\tt \#false}; the conditional deals with the first type
in the {\tt then} branch and the second type in the {\tt else} branch.  If a
mutator wraps {\tt (not $\cdot$)} around the test of the conditional, the
resulting mutant is ill-typed and, when run, this function eventually
causes a run-time type check to signal an impedance mismatch.
